Compiling refinement types to dependent types

### 2020-07-20 tex/paper.tex
Better context translation description

\paragraph{Contexts.}
As a warm-up,
we start with defining $\Tranctx$,
which is the simplest translation of the three.
It merely maps the types of the bindings in a (well-formed) context
from the surface language into the core language.

\begin{itemize}
  \item \ranchor{TCTX-Empty}.
    \begin{align*}
      & \inferrule{~}
                  {\emptyset \ctxok}
          \longmapsto
        \emptyset.
    \end{align*}
    The base case is trivial: we map the empty context to the empty context.
  \item \ranchor{TCTX-Bind}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\ \nonterm G \vdash \nonterm{ts}}
                  {\nonterm G , \gterm x : \nonterm{ts} \ctxok}
          \longmapsto
        \Tranctx(\nonterm G \ctxok), x : \tranty(\nonterm G \vdash \nonterm{ts}).
    \end{align*}

    We recurse on the prefix $\nonterm G$,
    which we are allowed to do due to the $\nonterm G \ctxok$ premise,
    and we use $\tranty$ to get the translated type of $\gterm x$,
    which we are also allowed to do due to the corresponding premise.
\end{itemize}

>>>>

\paragraph{Contexts.}
As a warm-up,
we start with defining $\Tranctx$,
which is the simplest of the three.
It merely maps the types of the bindings in a (well-formed) context
from the surface language into the core language.

Since $\Tranctx$ is defined on the derivations of $\nonterm G \ctxok$,
we consider the last rule used in a derivation:
\begin{itemize}
  \item \ranchor{TCTX-Empty}.
    \begin{align*}
      & \inferrule{~}
                  {\emptyset \ctxok}
          \longmapsto
        \emptyset.
    \end{align*}
    The base case is trivial: we map the empty context to the empty context.
  \item \ranchor{TCTX-Bind}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\ \nonterm G \vdash \nonterm{ts}}
                  {\nonterm G , \gterm x : \nonterm{ts} \ctxok}
          \longmapsto
        \Tranctx(\nonterm G \ctxok), x : \tranty(\nonterm G \vdash \nonterm{ts}).
    \end{align*}

    We recurse on the prefix $\nonterm G$,
    which is admissible due to the $\nonterm G \ctxok$ premise,
    and we use $\tranty$ to get the translated type of $\gterm x$,
    which is also admissible due to the other premise.
\end{itemize}
